Ricci-Ollivier curvature of two random walks on rooted phylogenetic subtree-prune-regraft graph

### 2015-02-20 curvature.tex
Typo.
exposition between degree and neighborhood lemmas

@@

@@

Next, we bound the number of neighbors shared by two adjacent trees.

@@

We first consider properties of the uniform random walk on the rSPR graph.
Assume that the random walk begins at a tree $T$.
The uniform random walk selects a tree uniformly at random from $N(T)$.
We denote the curvature of the uniform random walk between two trees $T$ and $S$ with $\curvature{T,S}$.
Recall that $\curvature{T, S} := 1 - \frac{W_1(m_T, m_S)}{d(x, y)}$.
For the uniform random walk, $m_T$ is simply the set of neighbors of $T$ with each assigned a mass of $\frac{1}{\degree{T}}$.

>>>>

We can improve these bounds in the case of adjacent trees.
To do so, we require the following lemma that characterizes exactly how the degree of a tree changes after an rSPR operation.

@@

Moreover, we can use these ideas to determine the number of SPR moves that are, in some respects, independent of a given SPR move.
That is, for two trees $S$ and $T$ differing by a single SPR move, we wish to know the number of SPR moves that are applicable to both trees rather than unique to one of the trees.
To formalize this concept, we consider pairs of trees $T' \in N(T)$ and $S' \in S(T)$ such that $\dspr{T',S'} = 1$.
The number of such ``squares'' involving two adjacent trees will play a key rule in our bounds on curvature, as they push the curvature of those trees towards 0.

@@

Next, we bound the number of neighbors shared by two adjacent trees.
The number of such "triangles" involving two adjacent trees has a key role in determining whether the curvature of two adjacent trees is positive or negative.

@@

We first consider properties of the uniform random walk on the rSPR graph.
Assume that the random walk begins at a tree $T$.
The uniform random walk selects a tree uniformly at random from $N(T)$.
We denote the curvature of the uniform random walk between two trees $T$ and $S$ with $\curvature{T,S}$.
Recall that $\curvature{T, S} := 1 - \frac{W_1(m_T, m_S)}{d(x, y)}$.
For the uniform random walk, $m_T$ is simply the set of neighbors of $T$ each assigned a mass of $\frac{1}{\degree{T}}$.
